19th International Satisfiability Modulo Theories Competition (SMT-COMP 2024): Rules and Procedures

### 2024-04-22 rules/rules24.tex
Adjusted dates in the SMT-COMP rules and worked on the ToDos that came from changing the execution service.

\title{18th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2023): Rules and Procedures}

@@

\begin{description}
\item[Mar~31] Deadline for new benchmark contributions.
\item[April~29] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~13] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[May~27] Deadline for final versions of solvers, including
  system descriptions.
\item[May~30] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~5-6] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2023 is part of the SMT Workshop~2023
(\url{http://smt-workshop.cs.uiowa.edu/2023/}),
which is affiliated with CADE~29 (\url{https://easyconferences.eu/cade2023/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state of the art in automated SMT problem
solving.

SMT-COMP 2023 will have seven tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
the \paralleltrack{} and the \cloudtrack{} (both sponsered by Amazon Web
Services), and an experimental \prooftrack{} focused on a qualitative evaluation
of different proof formats, proof checkers and proof-producing solvers.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific group of SMT-LIB logics.
%
We will recognize winners in all tracks but the \prooftrack{}.
%
They will be determined by the number of benchmarks solved (taking into account
the weighting detailed in Section~\ref{sec:scoring}); we will also recognize
solvers based on additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Antti Hyvarinen, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2023.
%

As in previous years, we have revised the rules slightly.  Some rule
changes in 2023 are designed to improve how logics are organized into
divisions. We have also added more divisions to the \mvaltrack and have defined a
new \prooftrack.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf Submission process.}  \emergencystretch.5cm \todo{Details}.
%
  \rationale{\todo{Details}}

  \item {\bf Move from StarExec to BenchExec.}  \emergencystretch.5cm \todo{Details}
%
  \rationale{\todo{Details}}
\end{itemize}

@@

\header{Solver execution.}
%
BenchExec (\url{https://github.com/sosy-lab/benchexec}) is a framework for reliable benchmarking and resource 
measurement developed by LMU's Software and Computational Systems Lab (SoSy-Lab \url{https://www.sosy-lab.org/}).
The framework itself can be downloaded and used locally by anyone. 
The competition itself will be executed on a BenchExec cluster owned by SoSy-Lab, 
who are kind enough to support our competition with their computing power. 
\todo{Is there a way for the users to run tests directly on the SoSy-Lab BenchExec cluster?}
%
%
%service enables members of the SMT research community to run solvers
%on jobs consisting of benchmarks from the SMT-LIB benchmark library.
%Jobs are run on a shared computer cluster.  The execution service is
%provided free of charge, but requires registration to create a
%login account.  Registered users may then upload solvers to
%run, or may run public solvers already uploaded to the service.
%Information about how to configure and upload a solver is contained in
%the StarExec user guide,
%\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2023.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

The StarExec service also limits the memory consumption of the solver
processes.  We expect the memory limit per solver/benchmark pair to be
on the order of 60\,GB.  The values of both the time limit and the
memory limit are available to a solver process through environment
variables.  See the StarExec user guide for more information.
\todo{What are the limits for BenchExec? Do we set limits ourselves?}

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2023/parallel-and-cloud-tracks.html}.

\header{Persistent State.}
%
Solvers may create and write to files and directories during the
course of an execution, but they must not read such files back during
later executions.  Each solver is executed with a temporary directory
as its current working directory.  Any generated files should be
produced there (and not, say, in the system's \texttt{/tmp}
directory).  The StarExec system sets a limit on the amount of disk
storage permitted---typically 20\,GB.  See the StarExec user guide for
more information.  The temporary directory is deleted after the job is
complete.  Solvers must not attempt to communicate with other
machines, e.g., over the network.
\todo{What are the limits for BenchExec? Do we set limits ourselves?}

@@

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~31, 2023}.
%
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~13, 2023}.

@@

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks
\textbf{except} the \paralleltrack and \cloudtrack
the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy / uninteresting benchmarks.}
  For the following tracks, all benchmarks that can be
  considered as easy or uninteresting based on the following criteria
  will be removed.
  \begin{itemize}
    \item \emph{\maintrack.} All benchmarks that were solved by all
      solvers (including non-competitive solvers) in less than one second in
          the corresponding track in 2018--2022.
    \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
  \end{itemize}

@@

SMT-COMP 2023 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France (chair)
\item \href{https://www.mpi-inf.mpg.de/departments/automation-of-logic/people/martin-bromberger}{Martin Bromberger}~-- MPI-INF, Germany
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Certora, Germany
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

>>>>

\title{19th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2024): Rules and Procedures}

@@

\begin{description}
\item[April~13] Deadline for new benchmark contributions.
\item[May~11] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~27] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~8] Deadline for final versions of solvers, including
  system descriptions.
\item[June~11] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~22-23] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2024 is part of the SMT Workshop~2024
(\url{http://smt-workshop.cs.uiowa.edu/2024/}),
which is affiliated with CAV~2024 (\url{https://i-cav.org/2024/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state of the art in automated SMT problem
solving.

SMT-COMP 2024 will have seven tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
the \paralleltrack{} and the \cloudtrack{} (both sponsered by Amazon Web
Services), and an experimental \prooftrack{} focused on a qualitative evaluation
of different proof formats, proof checkers and proof-producing solvers.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific group of SMT-LIB logics.
%
We will recognize winners in all tracks but the \prooftrack{}.
%
They will be determined by the number of benchmarks solved (taking into account
the weighting detailed in Section~\ref{sec:scoring}); we will also recognize
solvers based on additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Antti Hyvarinen, Jochen Hoenicke, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2024.
%

As in previous years, we have revised the rules slightly. Most changes are due to our move from StarExec to BenchExec.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}

  \item {\bf Move from StarExec to BenchExec.}  \emergencystretch.5cm
  The single query, incremental, unsat-core, model-validation and proof exhibition tracks 
  will no longer run on the StarExec platform hosted by the University of Iowa.
  Starting this year, we will run these tracks on the BenchExec cluster 
  (\url{https://github.com/sosy-lab/benchexec}) owned by LMU's Software 
  and Computational Systems Lab (SoSy-Lab \url{https://www.sosy-lab.org/}).
%
  \rationale{The StarExec cluster is in the process of being decommissioned. We picked 
             BenchExec as the new platform because it is host to similar competitions 
             and the experience collected there is a big help in our migration process.
             Moreover, it is in academic hands, so less likely to change conditions on
             short notice.}

  \item {\bf Submission process.}  \emergencystretch.5cm
  We changed the submission process from a Google form to a push request to the 
  SMT-COMP GitHub repository (\url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}). 
  Detailed instructions can be found in the README file there.
  Moreover, participants are now required to upload their final solver versions as a Zenodo 
  (\url{https://zenodo.org/}) submission that must contain a docker file that compiles the solver.
%
  \rationale{The change from Google form to GitHub push request makes it easier for us to 
             automatically create scripts for BenchExec. The submission of the final solver 
             versions to Zenodo makes it more likely that the competition results stay replicable.}

  \item {\bf Time limits.}  \emergencystretch.5cm
  The time limits for the cloud and parallel tracks are reduced to 2 minutes per problem.
%
  \rationale{The analysis of last years results showed that most problems in these tracks are solved quickly or not at all.}

  \item {\bf Memory limits.}  \emergencystretch.5cm
  The memory limits for the single query, incremental, unsat-core, model-validation and proof exhibition tracks are reduced to 30\,GB.
%
  \rationale{The reason are hardware limits of the new execution platform.}
\end{itemize}

@@

\header{Solver execution.}
%
BenchExec (\url{https://github.com/sosy-lab/benchexec}) is a framework for reliable benchmarking and resource 
measurement developed by LMU's Software and Computational Systems Lab (SoSy-Lab \url{https://www.sosy-lab.org/}).
The framework itself can be downloaded and used locally by anyone. 
The competition itself will be executed on a BenchExec cluster owned by SoSy-Lab, 
who are kind enough to support our competition with their computing power. 
To be more precise, the competition will be run on the 168 apollon nodes of the 
SoSy-Lab BenchExec cluster (for more details see \url{https://vcloud.sosy-lab.org/cpachecker/webclient/master/info}). 
It is also possible to locally emulate and test the computing environment on 
the competition machines using the following instructions: 
\url{https://gitlab.com/sosy-lab/benchmarking/competition-scripts/#computing-environment-on-competition-machines}.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2024.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

The \executionservice also limits the memory consumption of the solver
processes.  We expect the memory limit per solver/benchmark pair to be
on the order of 30\,GB.  The values of both the time limit and the
memory limit are available to a solver process through environment
variables.  See the user guide for the \executionservice for more information.

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2024/parallel-and-cloud-tracks.html}.

\header{Persistent State.}
%
Solvers may create and write to files and directories during the
course of an execution, but they must not read such files back during
later executions.  Each solver is executed with a temporary directory
as its current working directory.  Any generated files should be
produced there (and not, say, in the system's \texttt{/tmp}
directory).  The \executionservice sets a limit on the amount of disk
storage permitted---typically 20\,GB.  See the user guide for the 
\executionservice for more information.  The temporary directory is 
deleted after the job is complete.  Solvers must not attempt to 
communicate with other machines, e.g., over the network.
\todo{What are the limits for BenchExec? Do we set limits ourselves?}

@@

\header{Time Limit.}
This track will use a wall-clock time limit of 2 minutes per
solver/benchmark pair.

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf April~13, 2024}.
%
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~11, 2024}.

@@

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks
\textbf{except} the \paralleltrack and \cloudtrack
the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy / uninteresting benchmarks.}
  For the following tracks, all benchmarks that can be
  considered as easy or uninteresting based on the following criteria
  will be removed.
  \begin{itemize}
    \item \emph{\maintrack.} All benchmarks that were solved by all
      solvers (including non-competitive solvers) in less than one second in
          the corresponding track in 2018--2023.
    \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
  \end{itemize}

@@

SMT-COMP 2024 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France (chair)
\item \href{https://www.mpi-inf.mpg.de/departments/automation-of-logic/people/martin-bromberger}{Martin Bromberger}~-- MPI-INF, Germany
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Certora, Germany
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.
